---
title: "Creation of a FIFA Dashboard through a Shiny App"
author: "Rachel Anthony and Christian Sipley"
date: "2023-04-05"
output: html_document
---

In the RMD, we will be creating a Shiny Dashboard as a way to do exploratory data analysis and story telling for building the models to understand what variables play the biggest role in determining the winner of a FIFA 2023 World Cup match.


The package that allows the Shiny Dashboard to be built is `shinydashboard`. Run `install.packages("shinydashboard")` in the command line.

```{r import_lib}
library(shiny)
library(shinydashboard)
library(plotly)
library(dplyr)
```


```{r ui}
ui <- shinyUI(
  navbarPage(
    "2023 FIFA World Team Analysis",
    tabPanel(
      "EDA",
      fluidRow(
        column(
          width = 3,
          sidebarPanel(
            width = 12,
            selectInput(
              "team",
              "Choose a team:",
              choices = sort(unique(dfTeams$team.name))
            ),
            actionButton(
              "generate_graphic",
              "Generate Graphic",
              class = "btn-primary"
            )
          )
        ),
        column(
          width = 5,
          plotlyOutput("plot", width = "600px", height = "500px")
        ),
        fluidRow(
        column(
          width = 8,
           tableOutput("table"), style = "overflow-x: scroll"
        )
      ))),
        tabPanel("Index",
           p("The abbreviations used in the polar plot are:",style = "font-size:25px"),
           p("POS: Possession"),
           p("ATT: Total Attempts"),
           p("GIPA: Goals Inside the Penalty Area"),
           p("GOPA: Goals Outside the Penalty Area"),
           p("AST: Assists"),
           p("ONTA: On Target Attempts"),
           p("OFTA: Off Target Attempts"),
           p("AIPA: Attempts Inside the Penalty Area"),
           p("AOPA: Attempts Outside the Penalty Area"),
           p("LC: Left Channel"),
           p("LIC: Left Inside Channel"),
           p("CC: Central Channel"),
           p("RIC: Right Inside Channel"),
           p("RC: Right Channel"),
           p("TOR: Total Offers to Receive"),
           p("IHOR: Inbehind Offers to Receive"),
           p("IWOR: Inbetween Offer To Receive"),
           p("IFOR: Infront Offers to Receive"),
           p("RBMD: Receptions Between Midfield and Defensive Lines"),
           p("ALB: Attempted Line Breaks"),
           p("CLB: Completed Line Breaks"),
           p("ADLB: Attempted Defensive Line Breaks"),
           p("CDLB: Completed Defensive Line Breaks"),
           p("YC: Yellow Cards"),
           p("RC: Red Cards"),
           p("FA: Fouls Against Team"),
           p("OFF: Offsides"),
           p("PAS: Passes"),
           p("PASC: Passes Completed"),
           p("CRO: Crosses"),
           p("CROC: Crosses Completed"),
           p("SWOP: Switches of Play Completed"),
           p("COR:Corners"),
           p("FK: Free Kicks"),
           p("PS: Penalties Scored"),
           p("GP: Goal Preventions"),
           p("FT: Forced Turnovers"),
           p("DPA: Defensive Pressures Applied")
  )))
      
      
    

    
  


```

```{r scale_function}
#define function to scale values between 0 and 1
scale_values <- function(x){(x-min(x))/(max(x)-min(x))}


```

```{r scale_df}
dfScaledTeams <- 
  dfTeams %>% 
  mutate_at(-c(1,2,4,6,41,44), ~(scale_values(.)))
```

```{r r_tabular}
server <- function(input, output) {
  # get data based on team
  teamData <- reactive({
    dfScaledTeams %>%
      filter(team.name == input$team) %>%
      select(-c(1,2,4,6,41))
  })

  
   teamData_won <- reactive({
     teamData() %>%
       filter(result == "1") 
   })
  
   teamData_lost <- reactive({
     teamData() %>%
       filter(result == "0")  
   })

   won <- reactive({
     teamData_won() %>%
     summarise_if(is.numeric,mean)
   })
   
   lost <- reactive({
     teamData_lost() %>%
     summarise_if(is.numeric,mean)
   })
   
   
   output$table <- renderTable({
      # create a data frame with new row names
      table_data <- data.frame(
        Wins = as.numeric(won()),
        Losses = as.numeric(lost()),
        Difference = as.numeric(abs(won()-lost())) 
      ) 
      rownames(table_data) <- c("POS", "ATT", "GIPA", "GOPA", "AST", "ONTA", "OFTA",
                                "AIPA", "AOPA", "LC", "LIC", "CC", "RIC", "RC", "TOR",
                                "IHOR", "IWOR", "IFOR", "RBMD", "ALB", "CLB", "ADLB",
                                "CDLB", "YC", "RDC", "FA", "OFF", "PAS", "PASC", "CRO",
                                "CROC", "SWOP", "COR", "FK", "PS", "GP", "FT", "DPA")
      # transpose the data frame to create a tabular table
      
      table_data <- table_data[order(-table_data$Difference),]
      t(table_data)
    }, rownames = TRUE, colnames = TRUE)
   
   
   output$plot <- renderPlotly( {
    plot_ly(
      type = 'scatterpolar', mode = 'lines', fill = 'toself'
    ) %>%
      add_trace(
        r = as.matrix(won()[1,]),
        theta = c("POS", "ATT", "GIPA","GOPA","AST","ONTA","OFTA","AIPA","AOPA","LC","LIC","CC","RIC","RC","TOR","IHOR","IWOR","IFOR",
           "RBMD","ALB","CLB","ADLB","CDLB","YC","RDC","FA","OFF","PAS","PASC","CRO","CROC","SWOP","COR","FK","PS","GP","FT","DPA"),
        showlegend = TRUE,
        mode = "markers",
        name = "Won"
      ) %>%
      add_trace(
        r = as.matrix(lost()[1,]),
        theta = c("POS", "ATT", "GIPA","GOPA","AST","ONTA","OFTA","AIPA","AOPA","LC","LIC","CC","RIC","RC","TOR","IHOR","IWOR","IFOR",
           "RBMD","ALB","CLB","ADLB","CDLB","YC","RDC","FA","OFF","PAS","PASC","CRO","CROC","SWOP","COR","FK","PS","GP","FT","DPA"), 
        showlegend = TRUE,
        mode = "markers",
        name = "Lost",
        visible = "legendonly"
      ) %>%
      layout (
        polar = list(
          radialaxis = list(
            visible = T,
            range = c(0,1)
          )
        ),
        showlegend = TRUE
        
      )

    
  
 
})
}

```

```{r run_app}
shinyApp(ui, server)
```



